Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
drop remark about "semantic collisions"

Dealing with a large corpus of text faces both challenges: many samples,
and a very high dimensional space. In addition, the dimensionality
tends to increase with sample size, as the number of different words used
is greater in large corpuses. Beyond the mere size of the data matrix
created by a standard vectorization approach, as above, another challenge
is that the vectorization must be done in two passes over the documents,
as the size of the output vectors is not known beforehand.
Here, \emph{feature hashing} can be used
to tackle both of these challenges and produce a streaming vectorizer,
the {\tt HashingVectorizer} in scikit-learn.
The idea is to run words through a hash function, rather than a lookup table,
to map words to indices.
Collisions may occur, but the hashing algorithm \cite{weinberger2009}
is designed to mitigate their effect
(and because words often have multiple meanings,
``semantic'' collisions are inevitable in text processing tasks
\cite{attenberg2009}).
The dimensionality of the output vectors can be set by the user;
the bigger, the less likely collisions will occur.

>>>>

Dealing with a large corpus of text faces both challenges: many samples,
and a very high dimensional space. In addition, the dimensionality
tends to increase with sample size, as the number of different words used
is greater in large corpuses. Beyond the mere size of the data matrix
created by a standard vectorization approach, as above, another challenge
is that the vectorization must be done in two passes over the documents,
as the size of the output vectors is not known beforehand.
Here, \emph{feature hashing} can be used
to tackle both of these challenges and produce a streaming vectorizer,
the {\tt HashingVectorizer} in scikit-learn.
The idea is to run words through a hash function, rather than a lookup table,
to map words to indices.
Collisions may occur, but the hashing algorithm \cite{weinberger2009}
is specially designed to mitigate their effect.
The dimensionality of the output vectors can be set by the user;
the bigger, the less likely collisions will occur.
